Master's Research Proposal

### 2024-05-30 proposal/Proposal.tex
typo

However if you are interested in the rationales behind these objectives or diving into related work has already been done by others, the \textbf{Rationales} and \textbf{Related Work} sections are for you.

>>>>

However if you are interested in the rationales behind these objectives or diving into related work has already been done by others, the \textbf{Rationale} and \textbf{Related Work} sections are for you.
